
```{r echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
pacman::p_load(tidyverse,
               kableExtra)
```

# ICTWSS

The following variables are from the Institutional Characteristics of Trade Unions, Wage Setting, State Intervention and Social Pacts (ICTWSS) data base that contains information of 56 countries between 1960 and 2019. It provides information about collective bargaining, the different regulations and characteristics about the unions that every country has. The following table is divided by three categories in which we identified each variable: Economics Relationships and Employments, Pacts and Agreements and Political and Social Association.


```{r echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1aw_byhiC4b_0XPcTDtsCpCeJHabK38i4pCmkHshYMB8/edit#gid=0", range = c("B7:N216"), sheet= "Variables", col_names = F) %>%
  select(Variable = 1, Concept = 2, Definition = 4, Values = 5,  Class = 6, "Temporal coverage" = 7, "Regional coverage" = 8, Label = 13) %>% 
  arrange(Label) %>%
  knitr::kable(.) %>% 
  pack_rows("Economics Relationships and Employments", 1, 4, bold = T) %>% 
  pack_rows("Pacts and Agreements", 5, 59, bold = T) %>%
  pack_rows("Political and Social Association", 60, 210, bold = T) %>%
  kable_styling(font_size = 10) %>% 
  remove_column(8)

```

