```{r echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
pacman::p_load(tidyverse,
               kableExtra)
```

# OECD

The following variables are from Organisation for Economic Co-operation and Development (OECD) data base. It contains information of the different members of the organisation between 1960 and 2020. It provides information about Economics Relationships and Employments. Also, some variables that were extracted from WISE such as GDP and GNI per capita are included.

```{r oecd, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}

googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1aw_byhiC4b_0XPcTDtsCpCeJHabK38i4pCmkHshYMB8/edit#gid=0", range = c("B217:N279"), sheet= "Variables", col_names = F) %>%
select(Variable = 1, Concept = 2, Definition = 4, Values = 5,  Class = 6, "Temporal coverage" = 7, "Regional coverage" = 8, Fuente = 9, Label = 13) %>%
filter(grepl("_oecd", Variable)|grepl("OCDE-WISE", Fuente)) %>%
  select(-Fuente) %>% 
 arrange(Label) %>%
   knitr::kable(.) %>% 
  pack_rows("Economics Relationships and Employments", 1, 52, bold = T) %>% 
  kable_styling(font_size = 10) %>% 
  remove_column(8)


```

