```{r echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
pacman::p_load(tidyverse,
               kableExtra)
```

# World Bank

Some variables like employment share in different economic sectors, labour productivity and hourly labour productivity are from World Indicators of Skills for Employment (WISE) database. WISE was built with data from other well-known databases such as OECD and Eurostat to offer more statistical tools on skill development for different countries and in series of years from 1990 to the present.**CAMBIAR*

```{r wdi, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}

googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1aw_byhiC4b_0XPcTDtsCpCeJHabK38i4pCmkHshYMB8/edit#gid=0", range = c("B268:N309"), sheet= "Variables", col_names = F) %>%
  select(Variable = 1, Concept = 2, Definition = 4, Values = 5,  Class = 6, Label = 13) %>%
filter(grepl("_wdi", Variable)) %>% 
  arrange(Label) %>%
  knitr::kable(.) %>% 
  pack_rows("Economics Relationships and Employments", 1, 30, bold = T) %>%
  kable_styling(font_size = 10) %>% 
  remove_column(6)

```
