```{r echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
pacman::p_load(tidyverse,
               kableExtra)
```

# ILOSTAT

ILOSTAT is the primary source of labour statistics, containing variables about Economics Relationships and Employments as well as Political and Social Association, included in the following table. Some variables like employment share in different economic sectors, labour productivity and hourly labour productivity are from World Indicators of Skills for Employment (WISE) database. WISE was built with data from other well-known databases such as OECD and Eurostat to offer more statistical tools on skill development for different countries and in series of years from 1990 to the present.

```{r ilo, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
#ilostat
googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1aw_byhiC4b_0XPcTDtsCpCeJHabK38i4pCmkHshYMB8/edit#gid=0", range = c("B262:N628"), sheet= "Variables", col_names = F) %>% 
  select(Variable = 1, Concept = 2, Definition = 4, Values = 5,  Class = 6, "Temporal coverage" = 7, "Regional coverage" = 8, Label = 13) %>%
  filter(grepl("_ilo", Variable)) %>% 
  arrange(Label) %>%
  knitr::kable(.) %>% 
  pack_rows("Economics Relationships and Employments", 1, 282, bold = T) %>% 
  pack_rows("Political and Social Association", 283, 284, bold = T) %>%
  kable_styling(font_size = 10) %>% 
  remove_column(9)

```



# ILO-EPLEX

The ILO-EPLex database contains legal information about employment protection. In this database, we collected indicators about economic relationships and employment like the legal coverage of different jobs and characteristics of dismissal. These are available for 101 countries between 2010 and 2019.


```{r iloeplex, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
#ilo-eplex
googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1aw_byhiC4b_0XPcTDtsCpCeJHabK38i4pCmkHshYMB8/edit#gid=0", range = c("B323:N350"), sheet= "Variables", col_names = F) %>% 
  select(Variable = 1, Concept = 2, Definition = 4, Values = 5,  Class = 6, "Temporal coverage" = 7, "Regional coverage" = 8, Label = 13) %>% 
  arrange(Label) %>%
  knitr::kable(.) %>% 
  pack_rows("Economics Relationships and Employments", 1, 28, bold = T) %>%
  kable_styling(font_size = 10) %>% 
  remove_column(9)

```

